

```{r}
#| label: setup-soups-1
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Chicken Tortilla Soup

This is very easy to make, and I really enjoy it.

**Source:** From a former colleague.


**Ingredients:**


```{r}
#| label: chicken-tortilla-soup

dat <- tibble(
  Ingredients = c(
    "3-4 chicken breasts",
    "1 packet taco seasoning",
    "1 can corn",
    "1 can black beans",
    "1 small can tomato sauce",
    "1 small jar salsa",
    "1 can diced tomatoes"
  ),
  Tools = c(
    "Slow cooker / pressure cooker"
  )
)



dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=4, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Put the chicken into the cooker and cook until it can be shredded (slow cooker: 6-8 hours on low, pressure cooker: about 20 minutes).
2. shred the chicken.
3. Add the rest of the ingredients.
4. Let this cook for a short while, mainly to heat everything up.

**Variations:**

- The can of diced tomatoes is optional. I find it doesn’t really add that much.
- Adding cheese or sour cream after serving is quite good, though not necessary.


**Notes:**

- I like eating this with tortilla chips.
- Though I just kind of ... like eating tortilla chips.











