

```{r}
#| label: setup-soups-2
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Southwest Black Bean Soup

I tried to copy a store-made black bean soup that I liked. I think this is a solid soup.

**Source:** Going a bit from memory, a bit from a recipe that I don’t remember.


**Ingredients:**


```{r}
#| label: southwest-black-bean-soup

dat <- tibble(
  Ingredients = c(
    "3 cans black beans",
    "1-2 cans corn",
    "1-2 cans diced tomatoes with green chile peppers",
    "1 small red onion",
    "Olive oil",
    "1 sweet red pepper",
    "1-2 cans chicken brown (optional)",
    "1/2 cup jalapeno (optional)",
    "1 1/2 cups brown rice (optional)"
  ),
  Spices = c(
    "2-4 cloves garlic",
    "1-2 tbsp ground cumin",
    "2 1/2 tsp chile powder",
    "2 tsp red pepper flakes",
    "1 tsp paprika",
    "1-2 tsp corriander",
    "1 bay leaf (optional)",
    "Salt & black pepper to taste",
    ""
  ),
  Tools = c(
    "Large frying pan",
    "Blender",
    "Knife",
    "Cutting board",
    "",
    "",
    "",
    "",
    ""
  )
)



dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=4, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Sautee any of the fresh ingredients (onion, peppers, bay leaf, etc) in a large frying pan.
2. Add the rest of the ingredients and bring to boil, then reduce heat and allow to simmer for flavors to mix (~15 minutes minimum).
3. Puree approximately 1/3 of the soup, then return it to the pot and stir it in.

**Variations:**

- Add 3 tablespoons of fresh lime juice.
- If including rice, add that when you're eating it.


**Notes:**

- No need to drain the black beans, it just adds a bit of juice to the soup.
- You can blend one of the cans of beans (and some small amounts of other ingredients) independently, before adding them to the soup. I think the cooked beans blend better, though.










