

```{r}
#| label: setup-breakfast-other-1
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Bacon Sandwich


Yeah, a bacon sandwich is pretty basic. But I think there’s enough variants to make it worth putting here. And putting it here puts it in the index, which is a reminder for me.

**Source:** Who needs a source for this?


**Ingredients:**


```{r}
#| label: bacon-sandwich

dat <- tibble(
  Ingredients = c(
    "3-4 strips of bacon",
    "Bread, bun, or biscuit",
    "Mayonaise",
    "Other dressings as desired"
  ),
  Other = c(
    "Mustard",
    "Fried Egg",
    "Avocado/Guacamole",
    "Lettuce"
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") |> 
  style_tt( i=5, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Fry the bacon to your preference. Low/medium heat is better.
2. Toast the bread. You don’t have to, but ... toasted > not, so why wouldn’t you?




**Variations:**

- The recipe above is quite basic. The second column, “Other”, are some extra toppings that I like. They go well individually or together.
- Bananna pepper mustard might be hard to find, but it’s worth it. I encountered it in the WV/PA area. It's what got me to like mustard at all. I really liked the version by Backyard Gardens. The link I used to have is broken, there's a [recipie here](https://www.eatthismuch.com/calories/mustard-sweet-banana-pepper-sweet-and-mild-2382828) but I haven't tried it.



**Notes:**

- It’s a sandwich, how difficult can it be?



