

```{r}
#| label: setup-breakfast-sides-1
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Biscuits


Technically biscuits are more versatile than just using them for biscuits and gravy, but what’s the point? Actually, there is a point.


**Source:** [MinimalistBaker](https://minimalistbaker.com/the-best-damn-vegan-biscuits/)


**Ingredients:**


```{r}
#| label: biscuits

dat <- tibble(
  Ingredients = c(
    "1 cup milk",
    "1 - 2 tbsp apple cider vinegar",
    "280 - 290 g AP flour (~ 2 cups)",
    "1 tbsp baking powder",
    "1/2 tsp baking soda",
    "1 tsp salt",
    "4 tbsp butter"
  ),
  Tools = c(
    "Mixing bowl",
    "Measuring cups",
    "Mixing spoon/spatula",
    "Dough scraper",
    "Cast iron skillet",
    "",
    ""
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=5, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Preheat the oven to 450° F.
2. Mix the milk and apple cider vinegar (or lemon juice). This will simulate buttermilk. Let it stand for at least 5 minutes.
3. Whisk together dry ingredients.
4. Cut the butter (if you used sticks, which I suggest) into small chunks and mix it in with the flour. One of those butter-chopper things is great. Otherwise use your fingers, which isn't great.
5. Pour in the “buttermilk” mixture. Stir until just slightly combined, the dough will be very sticky.
6. Dump it out onto floured surface, dust the top with some flour, and fold the dough over itself a few times (4-6 should be fine). This is NOT kneading the dough. You’ll probably want to dust your hands with flour now and again. Or the dough scraper works well for this. Just try to handle the dough as little as possible. Otherwise you lose fluffiness and biscuits become more hard (I think).
7. Form the dough into a rough square/disk approximately 3/4 - 1 inch thick. Use a dough cutter, knife, or cookie cutter to cut out the biscuits. Place them in greased skillet. They can touch slightly.
7. Brush tops and sides of the biscuits with melted butter (another 1/2 - 1 tbsp).
8. Bake for 15-20 minutes, until the biscuits are fluffy and turning golden brown.
9. Eat those bad boys while they’re warm!




**Variations:**

I mean, it's biscuits, use them how you would otherwise. Some suggestions:

- Of course, biscuits and sausage gravy is phenomenal.
- Cinnamon roll biscuits are pretty great I actually like them better than “ordinary” cinnamon rolls.
- They work perfectly for biscuit sandwiches. Make these, fry up some sausage patties (or small strips of bacon). Throw a fried egg and some cheese on there. Some mayonnaise or mustard too if you like.
- Pimento cheese biscuit sandwiches.



**Notes:**

- You can use whole wheat flour instead of white. I tried 100% whole wheat flour once. It worked, but the biscuits were a bit more crumbly, so it was hard to make, e.g., a breakfast sandwich. A 50/50 blend worked pretty well. You may want to increase the amount of milk slightly, as the whole wheat flour seemed to absorb a bit extra liquid.
- If you're not dairy-free, you can use real buttermilk. And real butter.


