

```{r}
#| label: setup-breakfast-sides-2
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Home Fries


I think the name speaks for itself.

**Source:** I decided that frying potatoes couldn’t be *that* hard, so why buy bagged hash browns?


**Ingredients:**


```{r}
#| label: home-fries

dat <- tibble(
  Ingredients = c(
    "2-3 medium potatoes",
    "Cooking oil",
    "Spices/herbs"
  ),
  Tools = c(
    "Skillet",
    "Spatulas",
    ""
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=5, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Set your skillet (if you have one, frying pan if not) to heating. I tend to do this at medium to medium/high heat.
2. Dice up the potatoes. I usually make them into chunks about 1/4-1/2 inch. No need to peel them, just wash and cut off any roots that may have started growing.
3. Throw some high-heat oil (such as avocado oil) or bacon grease into the skillet, and the dump in the potatoes. 
  - You don't want TOO much oil, enough to coat all the chunks, but not so much that they're sitting in a pool of oil.
  - I mean, you CAN have them sitting in a pool. They'll be delicious, but they'll take longer.
  - Be careful of oil/grease splattering when you dump the potato in. 
  - Stir the potatoes around to get them all coated with the oil, and then spread them as evenly as you can.
4. Occasionally stir the potatoes around so that they get crisped on all sides (this is the reason for the medium/high heat). I found that using 2 spatulas helps with flipping them around.





**Variations:**

- Sprinkle with seasoned salt, salt, pepper, garlic, or other spices/herbs you like. I usually use seasoned salt.



**Notes:**

- By “occasional stirring” I mean give the potatoes at least a few minutes to develop a crisp before stirring/tossing them to get another side on the heat. I probably let them sit for about 3-5 minutes, stir them up, and let them sit another 3-5 minutes. After that you can toss them more frequently if you like.
- All told, I think they cook for 10-15 minutes. When I’m using home fries as a side, I put them on the stove first, and I take them off last. But I like crispy potatoes, you’re welcome to make an inferior version.





