

```{r}
#| label: setup-breakfast-sides-3
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Sausage Gravy


A staple of the South, this is basically a must-have to go along with biscuits.


**Source:** Passed-down directions and watching my wife make it.


**Ingredients:**


```{r}
#| label: sausage-gravy

dat <- tibble(
  Ingredients = c(
    "1/2 - 1/3 lbs ground breakfast sausage",
    "1-2 cups AP Flour",
    "Milk",
    "spices (see below)"
  ),
  Tools = c(
    "Skillet",
    "Spatulas",
    "",
    ""
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=5, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. In the pan/skillet, fry the sausage. Smash it a bit to make it produce more grease. The more the better. Feel free to add additional bacon grease.
2. Add the flour first. Sprinkle it around evenly and get it to absorb the great and cook a little.
3. Start adding milk and stirring to incorporate the flour. This can take a bit, that's why I didn't put an amount in the directions. Just keep adding milk until you have the consistency that you want.
4. Add spices to taste.
5. Put it on fresh biscuits and ~~get fat~~ enjoy.


- Some of the typical spices to use are: Seasoned salt, black pepper, garlic powder, a touch of cayane pepper.
- Don't be shy with them. Gravy is good with a bit of kick. Better than it being bland.





**Variations:**

- Use bacon instead of sausage. Not as great with the resulting gravy, in my opinion, but is a source of grease. Plus, you get bacon.
- If the sausage didn’t break up at all, you may want to add some bits of the sausage back into he gravy.



**Notes:**

- Breakfast sausage comes in many forms. I try to avoid links or pre-made patties, as I think they tend to produce less grease, and less little bits of sausage that fall off to get mixed in with the gravy.
- Don’t use sweetened or flavored milk (alternative milks often have this). It’ll still *work*, but it definitely changes the flavor in a way that I don’t really like.



