


```{r}
#| label: setup-pizza-1
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Pizza Dough


Maybe this belongs in the bread section, I don’t know. But it’s not really intended to be it’s own thing, so I’m putting it here. Don’t like it? Go make your own cookbook. Or just use a different one. Whatever.

**Source:** Several that I sort of amalgamated, mainly
[AllRecipes](https://www.allrecipes.com/recipe/20171/quick-and-easy-pizza-crust/), with some elements of 
[Food.com](https://www.food.com/recipe/restaurant-style-pizza-dough-recipe-by-weight-409380), 
[Sugardishme](https://www.sugardishme.com/10-minute-pizza-dough/), and probably something from
[Flour, Water, Salt, Yeast](https://kensartisan.com/flour-water-salt-yeast)?




**Ingredients:**


```{r}
#| label: pizza-dough

dat <- tibble(
  Ingredients = c(
    "425 g bread flour",
    "300 g warm water",
    "1 - 2 1/4 tsp yeast",
    "9 g salt",
    "1-2 tbsp olive oil (optional)"
  ),
  Tools = c(
    "Large mixing bowl",
    "Spatula",
    "Olive oil spray",
    "",
    ""
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=4, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Add the flour, yeast, and salt to the mixing bowl, and mix.
2. (Optional) Pour 1-2 tbsp oil over the flour.
3. Pour in the water and mix until the dough comes together.
4. Dump the dough out onto a work surface. I use a silicon mat and I don't flour it.
5. Knead for several minutes. Mainly make sure all the flour gets incorporated, and then work the dough a little more until it becomes somewhat smooth/elastic.
6. Spray the mixing bowl with olive oil, return the dough to the bowl. Turn over once or twice to get a coat.
7. Cover with a tea towel and let rest. 
8. After 30 mins - 1 hour, do a set of "stretch and fold" on the dough. Then let rest for another 30 min - 1 hour. After that the dough *can* be rolled out, though longer time to rise is better.

When ready to make the pizza:

9. Lightly flour the work surface and dump the dough out.
10. Sprinkle a bit more flour on top, and/or lightly flour your hands. Then pat the dough out a bit.
11. Roll out with a rolling pin. See Types of Crust below for several strategies here.




**Variations:**

- You can skip the oil if you want.
- Less yeast = more rise time. 
  - If you need the dough "quickly", this can be ready in about 1.5 - 2 hours. Just err on the side of more yeast (can probably go up to 3 tsp if you want).
  - If you have more time / plan things in advance, using less yeast (or sourdough starter!) and starting the day before will give more time and flavor.
  - Usually I'm lazy and use about 1 - 1.5 tsp yeast, and start the dough around noon if I want to make the pizza around 5:00pm or 6:00pm.


**Notes:**

- I use a silicone spatula for mixing and kneading the dough.
  - The dough doesn't stick as much to that as it does to a wooden spoon or my fingers.
  - To knead, I basically try to scoop a bit under the dough and fold it over itself.
- Avocado oil works just as well. For baking I don't think it really matters.


**Types of Crust**

There are several crust types. The best is obviously Detroit style pizza. Second is probably New York style. 
If you like Chicago style, well, that's your opinion. But opinions can be wrong, and yours is wrong.
If you like [Altoona-style pizza](https://en.wikipedia.org/wiki/Altoona-style_pizza), then ~~I apologize but~~ I kindly request that you close this browser and never return to this webpage.


Detroit-style

- For the crust, the main characteristic is a thick, airy, chery crust, almost like focaccia. To accomplish this you need to let the dough rise again after rolling it out.
- I'm a savage and don't have the proper dish, but I have a Lodge cast-iron baking sheet with nice edges. To make this, I do the following:
  - Gently roll (so you don't pop all the air bubbles) the dough out on your work surface, then work with your hands and the rolling pin to stretch the dough a bit more to approximately the correct size.
  - Put the dough into your baking pan, use a pizza slicer to chop off excess, so that the dough doesn't run up the edges (much). The excess can be used for garlic bread.
  - Cover with a tea towel and let the dough rise for another 1-2 hours. You may want something to keep the towel from laying directly on the dough. I use a wire bread cooling rack.
  - You can, and probably should, partially bake the dough before adding toppings. I'm usually lazy and don't do that.
- The cheese should go to the edge of the pan, so that it gets a nice crust on it. This is the epitome of pizza. Enjoy.

New York (maybe?) style

- This tends to be more thin-crust from my experience. Roll the dough out, toss it on your baking sheet, add toppings, and bake it.
- Ideally leave a little room at the edge to get a nice chewy crust. I haven't perfected that yet, so stay tuned. Maybe getting a pizza oven will help?
- I'm not a New Yorker, so (1) Don't crucify me; and (2) If you have tips, let me know.






