


```{r}
#| label: setup-pizza-3
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Garlic Bread


Garlic bread is is to pizza as Robin is to Batman.


**Source:** I worked at a pizzaria one summer.


**Ingredients:**


```{r}
#| label: garlic-bread

dat <- tibble(
  Ingredients = c(
    "Extra pizza dough",
    "Butter",
    "Garlic powder",
    "Parsley",
    "Salt"
  ),
  Tools = c(
    "Rolling pin",
    "Knife",
    "Baking sheet / cast iron skillet",
    "",
    ""
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=4, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Make the pizza dough. The amounts I listed should accommodate an ordinary cookie sheet pizza, and have some leftover dough.
2. Collect the scrap dough and form a dough ball. This will take a little bit to properly incorporate the scraps together.
3. Roll out the new dough ball. You can roll it very thin if you like.
4. Slather the top with butter. Like, a lot of it. It’s difficult to have too much here, I’m not sure that I’ve ever done so.
5. Sprinkle with garlic powder (a lot), parsley (some), and salt (some). Very precise, I know.
6. Set aside as the pizza cooks. The garlic bread should start to rise a bit, which is good.
7. When the pizza is done, bake the garlic bread for approximately 7 minutes. I think it’s done before all of the butter has cooked off. If it gets to that point, it usually means the garlic bread will be a bit more dry and/or crispy. Which, hey, if that’s what you like, more power so you. I don’t think this type of garlic bread is suited to being overly crispy.




**Variations:**

- You can’t go wrong adding cheese (mozzarella and/or Provolone, naturally). Or a grated cheese like Parmesan or Romano once it’s done baking.




**Notes:**

- For the salt, it’s better if you have the style with larger grains/crystals (sea salt or other varieties mistakenly called sea salt, such as rock salt). This type of salt will get you the nice texture.
- If you’re in a hurry and don’t want to make the dough (or don’t have any extra), you can use a French bread instead. Cut it in half as if you’re making a sub sandwich and load it with butter. I like to cut 1-2 grooves lengthwise to get more butter into the bread.
- If you’re being exceptionally lazy, hot dog buns also work. But I'll judge you and so will your guests.










