


```{r}
#| label: setup-pizza-2
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Pizza Sauce


Spoiler alter: The pizza sauce is basically just tomato sauce with a bunch of “Italian” herbs added, plus some salt, garlic, and red pepper flakes.

**Source:** Made this one up. Also vaguely remember some of the ingredients from when I worked at a pizzeria. I also remember the boss being cagey and glancing to make sure I wasn't trying to "steal" the recipe when I was working in the same room when he made the sauce. I wasn't ... but he also kept all the ingredients right there, and basically just dumped everything in a bowl and then I added that to the tomato sauce, so some of it was pretty obvious. He also drive a 1980s Mercedes limo around as his main car


**Ingredients:**


```{r}
#| label: pizza-sauce

dat <- tibble(
  Ingredients = c(
    "8-10 oz tomato sauce",
    "2 tsp oregano",
    "1/2 tsp parsley",
    "1 tsp garlic powder",
    "1/2 tsp salt"
  ),
  ingrd2 = c(
    "1/4 tsp onion powder",
    "3/4 tsp rosemary",
    "3/4 tsp basil",
    "1/2 tsp black pepper",
    "1/2 tsp red pepper flakes"
  ),
  Tools = c(
    "Small bowl",
    "Whisk or spoon",
    "",
    "",
    ""
  )
)


dat |> 
  setNames( c("Ingredients", " ", "Tools") ) |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") # |> 
  # style_tt( i=4, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Empty the tomato sauce into a bowl.
2. Add the herbs and spices.
3. Mix it well.





**Variations:**

- I think at least the first column of herbs and spices should be included. The second column is a bit less important.
- The herb/spice amounts were largely just guessing how much we normally used. Adjusting them will not change too much. I would recommend not going light on the oregano, though.
- If you want to make it thicker, add a small can of tomato paste as well. Though this will add volume, so you may want to put it in a pan and simmer it down a bit.
- Some recipes I looked up (but didn’t really copycat) also included some olive oil. I sometimes spray the dough before putting the sauce on, so I might get the same effect there.



**Notes:**

- This amount is good for a pizza the size of a regular baking sheet.
- It may help to mix everything and actually simmer it for a bit. I usually don’t.









