

```{r}
#| label: setup-breakfast-1
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Dutch Baby

A Dutch baby is kind of a weird hybrid between a pancake and french toast, maybe. I like it, though I prefer waffles or french toast.


**Source:** I don’t remember.


**Ingredients:**


```{r}
#| label: dutch-baby

dat <- tibble(
  Ingredients = c(
    "1/2 cup flour",
    "1/2 cup milk",
    "3 eggs",
    "1-2 tbsp sugar",
    "4 tbsp butter",
    "1/2 - 1 tsp vanilla extract",
    "1/2 tsp salt",
    "1 tsp cinnamon"
  ),
  Tools = c(
    "Cast iron skillet",
    "Mixing bowl",
    "Whisk",
    "Topping",
    "Powdered sugar",
    "Syrup (maple)",
    "Fried chicken",
    "Fruit"
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") |> 
  style_tt( i=4, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 

# Above makes the table. When eventually pushing this to the web, see if I can get the borders to work properly

```



**Directions:**

1. Preheat oven to 425° F.
2. Put butter in skillet and place in oven to melt.
3. Mix all of the other ingredients in a mixing bowl.
  - Once butter is melted and skillet it warm, remove from oven, pour in batter, and return to oven.
  - The skillet should be warm/hot, so that there is an immediate crisping of some of the batter. The whole thing will puff up a lot, but then collapse once you take it out.
4. Bake for 20 minutes. Then reduce temp to 300° and bake 5 more minutes.


**Variations:**

- Change the amount and/or type of spice to suit your taste. I like cinnamon, nutmeg works. Maybe thyme if you’re weird.


**Notes:**

- Nothing yet.



