


```{r}
#| label: setup-breakfast-3
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```




## Pancakes

Pankcakes are, well, they’re okay.

**Source:** I don’t remember.


**Ingredients:**


```{r}
#| label: pancakes-breakfast

dat <- tibble(
  Ingredients = c(
    "1 1/2 cups flour (??? g)",
    "2 tbsp sugar (??? g)",
    "1/2 tsp salt (4-5 g)",
    "1 1/2 - 2 tbsp baking powder",
    "1 eggs",
    "1 1/4 cup milk",
    "3 tbsp oil",
    "2 tsp vanilla extract"
  ),
  Tools = c(
    "Mixing bowl x2",
    "Whisk",
    "Measuring cups",
    "Frying pan",
    "Spatula",
    rep("",3)
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") 


```



**Directions:**

1. Set the pan on medium heat to start warming.
2. Beat the eggs, add the rest of the wet ingredients (milk, oil, vanilla) and mix.
3. Whisk the dry ingredients (flour, salt, sugar, baking powder) together. I usually do this seperately, but that probably doesn’t matter.
4. Add the wet ingredients to the dry, and mix, but leave a bit lumpy. Or mix until smooth. It doesn’t matter that much.
5. Put however much you want into the pan at a time. Usually 1/2 - 3/4 cup is good.
6. Flip when the surface gets bubbly.

**Variations:**

- None that I’ve experimented with. I don’t eat pancakes often.


**Notes:**

- Nothing yet.


