

```{r}
#| label: setup-breakfast-4
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```



## Waffles


Of the breakfast foods made with batter, waffles are the best. Crispy on the outside, soft on the inside, and you can pair it with fruit, syrup, or breaded chicken.

This recipe should make 4-8 waffles, depending on the size of your waffle iron.


**Source:** Allrecipes, though the link I used for them is broken.


**Ingredients:**


```{r}
#| label: waffles

dat <- tibble(
  Ingredients = c(
    "320 g flour (2 cups)",
    "40 g sugar (3 tbsp)",
    "9 g salt (1/4 - 1 tsp)",
    "4 tsp baking powder",
    "2 eggs",
    "400 g milk (1 3/4 cup)",
    "1/2 cup oil",
    "1/2 - 1 1/2 tsp vanilla extract"
  ),
  Tools = c(
    "Mixing bowl x2",
    "Whisk",
    "Measuring cups",
    "Waffle iron",
    "Topping",
    "Butter & Syrup (maple, of course)",
    "Fried chicken",
    "Fruits and whipped cream"
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") |> 
  style_tt( i=5, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Set the waffle iron to start heating up.
2. Beat the eggs, then add the rest of the wet ingredients (milk, oil, vanilla) and mix.
3. Whisk the dry ingredients (flour, salt, sugar, baking powder) together. I usually do this separately, but that probably doesn’t matter.
4. Add the wet ingredients to the dry, and mix well.



**Variations:**

- For Sourdough Waffles: Use 300 g starter. Reduce milk to 300 g and flour to 175 g.
- A different version of yeasted waffles, which doesn’t require a sourdough starter, is found at post number 5 by [“Queen Bruin” here](https://boards.straightdope.com/t/alton-browns-waffles-were-a-little-disappointing-dopers-give-me-great-waffles/409415). I tried it once and didn’t find it worth the effort.


**Notes:**

- Don’t always trust the time on the waffle iron. I just let it cook until it’s basically done steaming, or a bit more.
- About egg substitutes:
  - When using powdered egg substitute, my waffles have always torn open.
  - At some point I might experiment with amounts, or some other tweaks.
  - I haven't tried JUST Egg in waffles yet.
  
- TODO: Measure my waffle iron. Approx 3/4 cup of batter.



