

```{r}
#| label: setup-breakfast
#| results: false
#| output: false


library("tidyverse")
library("tinytable")



tlwd <- 0.125
bgcol <- "grey60"
bgcol <- "skyblue4"



```





## French Toast



**Source:** [Serious Eats](https://www.seriouseats.com/perfect-quick-easy-french-toast). They experimented, and I like their conclusions.

**Ingredients:**


```{r}
#| label: french-toast

dat <- tibble(
  Ingredients = c(
    "2 eggs",
    "2/3 cup milk",
    "1/2 tbsp sugar"
  ),
  Tools = c(
    "Mixing bowl",
    "Whisk",
    "Frying pan"
  )
)


dat |> 
  tt(  theme = "striped" ) |> 
  style_tt( i=0, background=bgcol, color="white") |> 
  style_tt( i=4, j=2, background=bgcol, color="white", bold=TRUE )
  # style_tt( i=0, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=1, line = "t", line_color="black", line_width = tlwd) |> 
  # style_tt( i=8, line = "b", line_color="black", line_width = tlwd) |> 
  # style_tt( i=4, j=2, line = "t", line_color="black", line_width = tlwd )  |> 
  # style_tt( i=4, j=2, line = "b", line_color="black", line_width = tlwd )  |> 


```



**Directions:**

1. Set the pan to medium to start heating.
2. Whisk the eggs, then add the rest of the ingredients besides bread.
3. Sprinkle a little bit of sugar on the wet part of the batter when frying. It will carmalize and form a crisp little crust. But be CAREFUL, it will burn easily.

**Variations:**

1. Add some cinnamon to the batter. I forget how much I use, will update next time I made french toast.


**Notes:**

- Recipie can be easily increased or decreased.
  - The egg-to-milk ratio should be approximately 1/3 cup of milk for each egg (or possibly slightly less, maybe 1/4 cup milk for each egg).
  - The sugar-to-egg ratio should be about 1/4 tbsp sugar per egg.
- I've not yet tried this with JUST Egg.






